### 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
Added metric units, interior dimensions, sofa HRR

\section{Experimental Test Arrangement}
The experiments were conducted in a two story structure that was built to simulate a townhouse with a walk out basement. The structure was built on a concrete slab. The lower level of the structure had an outer wall composed of 2~ft thick interlocking concrete blocks. The joints and gaps between the blocks were filled with high temperature foam insulation. The interior walls of the lower level were framed with steel studs and track. The studs were set to 0.40~m (16~in.) centers. The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in.) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in.) x 44~mm (1.75~in.) and an 11~mm (0.43~in.) thick oriented strand board web. Tongue and grove, 18.3~mm (0.72~in.) thick, oriented strand board was screwed to the top of the TJIs to form the floor of the upper level. The walls and ceiling of the lower level was composed of two layers of 12.7~mm (0.5~in.) thick cement board.

@@

The interior footprint of both the upper and lower level are each approximately 20~ft wide by 36~ft deep. 	Figures~\ref{fig:schematic_low} and \ref{fig:schematic_up} are schematics of the floor plans of the upper and lower levels. In these images, circles indicate the location of thermocouples, squares indicate the location of velocity probes and thermocouples, diamonds indicate gas measurement probes, and triangles indicate the location of heat flux measurements.

@@

On Side C of the lower level, there is a set of doors with a total opening of approximately 72~in. wide and 80~in. high. These doors were open for the duration of the hose exposure experiments.

@@

\section{Fuel Load}
The interior finish of the lower level consisted of 1/2~in. oriented strand board (OSB).  The OSB covered the entire ceiling, floor and the walls on Sides A, B, and D. Polyolefin carpeting over polyurethane foam padding covered the floor of the lower level.  The fuel load in the basement consisted of three sofas, oriented strand board on the ceiling and walls of the basement (cf. Fig.~\ref{fig:schematic_low}).

@@

The heat flux gauges used in the lower level were Schmidt-Boelter type, water cooled gauges.  Total heat flux was measured with Schmidt Boelter gauges. Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
\caption{Schematic showing the test arrangement on the lower level. The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional probes in the open doorway on Side C.}
\label{fig:test_plan}
\end{figure}

>>>>

\section{Experimental Test Arrangement}
The experiments were conducted in a two story structure that was built to simulate a townhouse with a walk out basement. The structure was built on a concrete slab. The lower level of the structure had an outer wall composed of 0.6~m (2~ft) thick interlocking concrete blocks. The joints and gaps between the blocks were filled with high temperature foam insulation. The interior walls of the lower level were framed with steel studs and track. The studs were set to 0.40~m (16~in.) centers. The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in.) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in.) x 44~mm (1.75~in.) and an 11~mm (0.43~in.) thick oriented strand board web. Tongue and grove, 18.3~mm (0.72~in.) thick, oriented strand board was screwed to the top of the TJIs to form the floor of the upper level. The walls and ceiling of the lower level was composed of two layers of 12.7~mm (0.5~in.) thick cement board.

@@

The interior footprint of the lower level is approximately 5.7~m (18.7~ft) wide by 10.6~m (34.8~ft) deep. The interior area of the upper level is approximately 6.0~m (19.8~ft) wide by 11~m (36~ft) deep.	 Figures~\ref{fig:schematic_low} and \ref{fig:schematic_up} are schematics of the floor plans of the upper and lower levels. In these images, circles indicate the location of thermocouples, squares indicate the location of velocity probes and thermocouples, diamonds indicate gas measurement probes, and triangles indicate the location of heat flux measurements.

@@

On Side C of the lower level, there is a set of doors with a total opening of approximately 1.8~m (6~ft) wide and 2.0~m (6.7~ft) high. These doors were open for the duration of the hose exposure experiments.

@@

\section{Fuel Load}
The interior finish of the lower level consisted of 12.7~mm (1/2~in.) oriented strand board (OSB).  The OSB covered the entire ceiling, floor and the walls on Sides A, B, and D. Polyolefin carpeting over polyurethane foam padding covered the floor of the lower level.  The fuel load in the basement consisted of three sofas, oriented strand board on the ceiling and walls of the basement (cf. Fig.~\ref{fig:schematic_low}).  In a free burn condition, each sofa can generate a peak heat release rate of approximately 2~MW.

@@

The heat flux gauges used were Schmidt-Boelter type, water cooled gauges.  Total heat flux, convection and radiation, was measured with the uncovered gauge. Radiant heat flux was measured with a gauge covered with a sapphire lens.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
\caption{Schematic showing the test arrangement on the lower level. The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional velocity probes in the open doorway on Side C.}
\label{fig:test_plan}
\end{figure}
